Twisted 11-dimensional supergravity, I

### 2021-09-28 dimred.tex
update

In diagrammatic detail, the potential theory we are considering has underlying cochain complex of fields
\beqn\label{eqn:IIApot}
\begin{tikzcd}
- & + \\ \hline
& {\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) }_\eta  \\
{\PV^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\mu \arrow[r, "u\div"] & u{\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\nu \\
u^{-1}{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\div"] & {\Omega^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
\end{tikzcd}
\eeqn.

@@

\begin{conj}
\label{conj:5dsugra}
The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representations $V$ has BV fields
\begin{itemize}
\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate fields $\eta, B_{grav}$,
\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate field $B$,
\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate field $\psi$.
\end{itemize}

>>>>

In diagrammatic detail, the potential theory we are considering has underlying cochain complex of fields
\beqn\label{eqn:IIApot}
\begin{tikzcd}
- & + \\ \hline
& {\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) }_\eta  \\
{\PV^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\mu \arrow[r, "u\div"] & u{\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\nu \\
u^{-1}{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\del"] & {\Omega^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
\end{tikzcd}
\eeqn.

@@

\begin{conj}
\label{conj:5dsugra}
The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representation $V$ has BV fields
\begin{itemize}
\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate fields $\eta, B_{grav}$,
\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate field $B$,
\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate field $\psi$.
\end{itemize}

### 2021-09-28 draft.tex
update

\title{Twisted 11-dimensional supergravity, I}
\author{Surya Raghavendran}
\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
Waterloo, Ontario N2L 2Y5\\ Canada}
\email{??}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
to do
\end{abstract}
\maketitle
\newpage

@@

%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris

@@

\section{The non-minimal twist}

We have provided numerous consistency checks that the 11-dimensional theory defined on $\CC^5 \times \RR$ is a twist of supergravity. 
We have referred to this theory as holomorphic as it depends on the complex structure in the maximal number of directions. 
In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.

On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one in the holomorphic twist. 
We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
\[
A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
\]
where $\Pi$, as always, denotes parity shift.
The equations of motion are of the form
\[
\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
\]
The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
We give a precise definition below.

More generally, the twist can be defined \brian{finish}

@@

\subsection{The non-minimal supercharge}

Let $Q^{hol}$ denote the fixed holomorphic supercharge. 
We have argued in \S \ref{s:residual} that the $Q^{hol}$-cohomology of the 11-dimensional supersymmetry algebra is a symmetry of our proposed holomorphic twist of 11-dimensional supergravity.

There is a twist of supergravity which can be witnessed as a further deformation of the $Q^{hol}$-twist. 
\brian{fix this}

Recall that the odd component of this residual supersymmetry algebra is
\[
\wedge^2 L \cong \wedge^2(\CC^5) 
\]
which we can identify with constant coefficient holomorphic $(2,0)$ forms on $\CC^5 \times \RR$ (they are zero-forms along the $\RR$-direction). 
Because these forms are constant coefficient, they are also closed, and hence lift to $(1,0)$ forms on $\CC^5 \times \RR$ in a way that is unique up to $\del$-exact terms.

Using this observation, we constructed an embedding of $\wedge^2(L)$ into the fields of supergravity. 
Explicitly, the element $z_i \wedge z_j \in \wedge^2 L$ was mapped to the $\gamma$-type field
\[
\Psi_{ij} = \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR) ,
\]
where $i,j=1,\ldots, 5$ and $i \ne j$.

\parsec[-]

The first main result of this section is to characterize the twist of our 11-dimensional theory on $\CC^5 \times \RR$ by the element $\Psi_{ij}$.

\brian{introduce PCS}
Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
\[
\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
\]

\begin{thm}
The $\Psi_{ij}$-twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
\[
\CC_{z_i} \times \CC_{z_j} \times \RR^7 .
\]
\end{thm}

Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.

The Lie algebra of gauge symmetries of this model on flat space is 
\[
\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
\]
which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.

\parsec[sec:nmsymmetry]
Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.

Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
\[
\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
\]
We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.

Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
\begin{align*}
[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
\end{align*}
where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.

From these relations, it is easy to see that any divergence-free vector field of the form:
\begin{itemize}
\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
\end{itemize}
are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.

Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
\[
H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
\]
Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
\[
0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
\]
where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.

\section{The twisted $\Omega$-background}

\subsection{$\Omega$-deformed symmetry algebra}

On flat space, we have

\subsection{M2 branes in the $\Omega$-background}

In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
\beqn\label{eqn:m2omega}
\{0\} \times \RR \subset \CC^2 \times \RR .
\eeqn

The field which sources this brane is a distributional differential form $F$.
The linear equation of motion for $F$ is the distributional equation 
\[
\d^2 z \wedge \dbar F = N \delta_{z=0} 
\]
where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.

The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
Explicitly, we can characterize it as follows.

\begin{prop}
The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
\[
F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
\] 
satisfies the non-linear equation of motion 
\[
\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
\]
\end{prop}
\begin{proof}
The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
\end{proof}

We can interpret $F$ geometrically in the following way. 
Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.

On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
\[
0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
\]
where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.

Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$. 
Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
\[
\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
\]

In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
\[
(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
\]
of the $(0,1)$-form
\[
F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
\] 
The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
\[
\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
\]

>>>>

\title{Twisted 11-dimensional supergravity, I}
\author{Surya Raghavendran}
\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
Waterloo, Ontario N2L 2Y5\\ Canada}
\email{??}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
to do
\end{abstract}
\maketitle

\tableofcontents

\newpage

@@

@@

@@

\input{nonmin}

### 2021-09-28 suco.tex
update

\begin{itemize}
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
It is mapped to the fields: 
\[
\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
\] 
\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
It is mapped to the fields: 
\[
\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
\] 
\end{itemize}

@@

The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$. 
Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above:
\begin{itemize}
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
\[
\d w_a \wedge \d w_b, \quad a,b=1,2,3,4. 
\] 
\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
\[
(z \d w_a  \wedge \d w_b + \ep^{abcd} w_c \d z \wedge \d w_d) , \quad a,b=1,2,3,4. 
\] 
\end{itemize}

@@

\item
The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
\item 
The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
\[
z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
\item 
The bosonic summand $\lie{sl}(2)$ is mapped to the triple
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\]
\end{itemize}

@@

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
It is mapped to the fields 
\[
z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
\] 
\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
It is mapped to the fields
\[
\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
\]
\end{itemize}

@@

>>>>

\begin{itemize}
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
It is mapped to the fields: 
\[
\frac{1}{2} (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4 .
\] 
\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
It is mapped to the fields: 
\[
\frac{1}{2} z (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
\] 
\end{itemize}

@@

The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$. 
Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
Recall, we are using the holomorphic coordinates $(z,w_1,\ldots,w_4)$ on $\CC^5$ where $z$ is the holomorphic coordinate along the $M2$ brane. 
\begin{itemize}
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
\[
\d w_a \wedge \d w_b, \quad a,b=1,2,3,4. 
\] 
\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
\[
z \d w_a  \wedge \d w_b + \frac12 \d z \wedge (w_a \d w_b - w_b \d w_a) , \quad a,b=1,2,3,4. 
\] 
\end{itemize}

@@

\item
The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
\item 
The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
\[
z_j \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
\item 
The bosonic summand $\lie{sl}(2)$ is mapped to the triple
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\]
\end{itemize}

@@

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
It is mapped to the fields 
\[
z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
\] 
\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
It is mapped to the fields
\[
\frac12 w_a (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
\]
\end{itemize}

@@

To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
Recall, we are using the holomorphic coordinates $(z_1,z_2,z_3, w_1,w_2)$ on $\CC^5$ where $z_i$ are the holomorphic coordinates along the $M5$ brane. 
\begin{itemize}
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
\[
\d z_i \wedge \d w_a, \quad i=1,2,3, \quad a=1,2. 
\] 
\item 
The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
\[
w_a \d z_i  \wedge \d z_j + \frac12 \d w_a \wedge (z_i \d z_j - z_j \d z_i) , \quad i,j=1,2,3, \quad a=1,2. 
\] 
\end{itemize}
